\vspace{-2cm}Formation Control of AAUSHIP

### 2015-04-12 paper.tex
JAL: Upd. fig. size
Fix emails

%\documentclass[a4paper,12pt]{IEEEtran}
\documentclass[a4paper,conference]{IEEEtran}
%\input{preamble}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage[utf8]{inputenc} % So we can input Nicks name in the paper title!
\usepackage[T1]{fontenc}
\usepackage{amsmath}%,amsfonts,amssymb} % Added so we can do pretty math equations.
\usepackage{geometry}
\usepackage{lipsum}
\usepackage[pdftex,bookmarks=true,bookmarksnumbered=true]{hyperref}
\usepackage[english,final]{varioref} % Vi kan anvende \vref
\usepackage[draft]{fixme}
\usepackage[boxed,linesnumbered]{algorithm2e}
%\usepackage{glossaries}
%\setacronymstyle{long-sc-short}
\geometry{left=3cm,right=3cm,bottom=4cm}
\newcommand{\colwidth}{3in}
\begin{document}

%\newacronym{FRP}{FRP}{Formation Reference Point}
%\newacronym{GNC}{GNC}{Guidance, Navigation and Control}
%\newacronym{LOS}{LOS}{Line-Of-Sight}
\title{\vspace{-2cm}Formation Control of AAUSHIP}
%\author{Nick Østergaard \and Jeppe Dam \and Jesper A. Larsen}
\author{\IEEEauthorblockN{Nick Østergaard}
\IEEEauthorblockA{Dep. of Electronic Systems\\Aalborg University\\Denmark} 
\and
\IEEEauthorblockN{Jeppe Dam}
\IEEEauthorblockA{Dep. of Electronic Systems\\Aalborg University\\Denmark}
\and
\IEEEauthorblockN{Jesper A. Larsen}
\IEEEauthorblockA{Dep. of Electronic Systems\\Aalborg University\\Denmark\\Email: jal@es.aau.dk}

@@

\begin{figure}[htbp]
  \includegraphics[width=.9\linewidth]{fig/ftotmagnfigpdf1}
	\caption{Plot of one agent's trajectory with a desired position with
		obstacles to avoid}
  \label{fig:potfieldagenti}
\end{figure}

A plot for a total potential reference field for a single agent can be
seen on figure \ref{fig:potfieldagenti}. The red line made of crosses
is the trajectory that one single agent will follow, if the obstacles
to avoid in the plot are static. In the plot every object, either
another agent or an object, are kept static. So it shows how the
trajectory will be in one single time step. This will change in the
next time step if the other agents also move in the potential field.
The agent avoids obstacles on the way, where it can be seen that it
does not get into the safety radius of the obstacles. In this specific
plot is a safety radius ($r$) of $20$m chosen, such that the distance
from agent $p_i$ (red trajectory) to any obstacle always will be
larger than $20$m.

@@

\begin{figure}[htbp]
  \includegraphics[width=.9\linewidth]{fig/ftotmagnfigpdf}
	\caption{Agent $i$ avoids agent $j$ and converges to the minima at
		the virtual leader}
  \label{fig:avoidagent}
\end{figure}

@@

\begin{figure}[htbp]
  \includegraphics[width=.9\linewidth]{fig/ftotmagnfigpdf3}
	\caption{An agent gets stuck due to a local minima between two other
	agents. The agent cannot get out of this minima unless the other two
	agents makes the space for the agent to pass through}
  \label{fig:roevproblem}
\end{figure}

@@

\begin{figure}[htbp]
  \includegraphics[width=.9\linewidth]{fig/ftotmagnfigpdf4}
	\caption{An agent that before was stuck now does not get into a
		local minima close to the agents, as it now sees the two other
		agents as one larger agent.}
  \label{fig:solroevproblem}
\end{figure}

Here the first solution is applied where the two agents, that were too
close to each other, have been clustered into one, seen from the
$i$'th agent. Now the local minima between the agents have been
neglected and the $i$'th agent can generate its trajectory around the
agents and continue to the endpoint of the potential field. The
algorithm checks if the distances between the agents are lower that $2
\cdot r$. If this is the case it means that the $i$'th agent cannot
generate a trajectory in between these agents, which can lead to a
local minima. Therefore is the agents that are too close combined into
one by generating the middle point between their positions and
generating a new radius. This makes a larger circle where the two
agents are in the subset. This circle will be larger depending on the
wanted safety radius thus rises the need to recheck the potential
field again after have generated a new combined agent. If the radius
of the new agent places it close to one of the single agents, these
also might need to cluster. Thus the algorithm needs to run until no
distances between agents are less than two times the radius.

@@

\section{Results}
The potential field control system consists of multiple elements
as seen with the flow which is illustrated on the block diagram on
figure~\vref{fig:potentialfield_block}.
\begin{figure}[htbp]
\centering
\includegraphics[width=\colwidth]{fig/potentialfield_block}
\caption{Block diagram showing the iteration process of using the
potential fields for computation of the input vector}
\label{fig:potentialfield_block}
\end{figure}
The first block is the potential field generator. This is the
potential field calculation to compute the magnitude of the global
potential field. This information is passed to a trajectory generator,
which generates the reference trajectory. This reference trajectory is
where the $i$'th agent needs to move. This is passed to the controller
of the vessel, which then computes the input to the actuators on the
vessels, which in this case is done via a linear controller, which has been developed based on a linearized version of the vessel around its nominal operating point. The position of the vessels are then fed back, both to the
potential field calculation, the trajectory generation and the
controller. The potential field needs to be calculated from the
vessels relative position, the trajectory generation needs the
position for the intermediate reference position and the controller
will need it for i.e. error calculations.

@@

A simulation of the algorithm with the dynamics of the AAUSHIP can be seen on figure \ref{fig:potform}.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\colwidth]{fig/lawn-bar-formation}
  \caption{Four agents are placed relative to the middle point of the
	formation, the virtual leader. This leader moves at the trajectory
with the waypoints, but only changes to the next waypoint if the
agents are in formation. The blue circles with the red plus signs are
the waypoints of the virtual leader. The other paths are computed from
this and the FRP.}
  \label{fig:potform}
\end{figure}
The red crosses are waypoints that have been targeted as the next waypoint to reach. The line connecting those waypoints are the virtual leader movement, which changes position from waypoint to waypoint to generate the straight line segments for the formation to follow. Every of the four agents have a relative position placement to the virtual leader, the agents positions are $p_{ij}$ and given as $p^n_{vl} + \text{offset}$ and the position of the virtual leader is given as $p^n_{vl}$. The ships are shown as yellow ships and the ships in formation is connected with a red line.

>>>>

%\documentclass[a4paper,12pt]{IEEEtran}
\documentclass[a4paper,conference]{IEEEtran}
%\input{preamble}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage[utf8]{inputenc} % So we can input Nicks name in the paper title!
\usepackage[T1]{fontenc}
\usepackage{amsmath}%,amsfonts,amssymb} % Added so we can do pretty math equations.
\usepackage{geometry}
\usepackage{lipsum}
\usepackage[pdftex,bookmarks=true,bookmarksnumbered=true]{hyperref}
\usepackage[english,final]{varioref} % Vi kan anvende \vref
\usepackage[draft]{fixme}
\usepackage[boxed,linesnumbered]{algorithm2e}
%\usepackage{glossaries}
%\setacronymstyle{long-sc-short}
\geometry{left=3cm,right=3cm,bottom=4cm}
%\newcommand{\colwidth}{3in}
\begin{document}

%\newacronym{FRP}{FRP}{Formation Reference Point}
%\newacronym{GNC}{GNC}{Guidance, Navigation and Control}
%\newacronym{LOS}{LOS}{Line-Of-Sight}
\title{\vspace{-2cm}Formation Control of AAUSHIP}
%\author{Nick Østergaard \and Jeppe Dam \and Jesper A. Larsen}
\author{\IEEEauthorblockN{Nick Østergaard}
\IEEEauthorblockA{Dep. of Electronic Systems\\Aalborg University\\Denmark\\Email: nickoe@es.aau.dk} 
\and
\IEEEauthorblockN{Jeppe Dam}
\IEEEauthorblockA{Dep. of Electronic Systems\\Aalborg University\\Denmark\\Email: jeppedam@es.aau.dk}
\and
\IEEEauthorblockN{Jesper A. Larsen}
\IEEEauthorblockA{Dep. of Electronic Systems\\Aalborg University\\Denmark\\Email: jal@es.aau.dk}

@@

\begin{figure}[htbp]
  \includegraphics[width=\linewidth]{fig/ftotmagnfigpdf1}
	\caption{Plot of one agent's trajectory with a desired position with
		obstacles to avoid}
  \label{fig:potfieldagenti}
\end{figure}

A plot for a total potential reference field for a single agent can be
seen on figure \ref{fig:potfieldagenti}. The red line made of crosses
is the trajectory that one single agent will follow, if the obstacles
to avoid in the plot are static. In the plot every object, either
another agent or an object, are kept static. So it shows how the
trajectory will be in one single time step. This will change dynamically in the
next time step if the other agents also move in the potential field.
The agent avoids obstacles on the way, where it can be seen that it
does not get into the safety radius of the obstacles. In this specific
plot is a safety radius ($r$) of $20$m chosen, such that the distance
from agent $p_i$ (red trajectory) to any obstacle always will be
larger than $20$m.

@@

\begin{figure}[htbp]
  \includegraphics[width=\linewidth]{fig/ftotmagnfigpdf}
	\caption{Agent $i$ avoids agent $j$ and converges to the minima at
		the virtual leader}
  \label{fig:avoidagent}
\end{figure}

@@

\begin{figure}[htbp]
  \includegraphics[width=\linewidth]{fig/ftotmagnfigpdf3}
	\caption{An agent gets stuck due to a local minima between two other
	agents. The agent cannot get out of this minima unless the other two
	agents makes the space for the agent to pass through}
  \label{fig:roevproblem}
\end{figure}

@@

\begin{figure}[htbp]
  \includegraphics[width=\linewidth]{fig/ftotmagnfigpdf4}
	\caption{An agent that before was stuck now does not get into a
		local minima close to the agents, as it now sees the two other
		agents as one larger agent.}
  \label{fig:solroevproblem}
\end{figure}

Here the first solution is applied where the two agents, that were too
close to each other, have been clustered into one, seen from the
$i$'th agent. Now the local minima between the agents have been
neglected and the $i$'th agent can generate its trajectory around the
agents and continue to the endpoint of the potential field. The
algorithm checks if the distances between the agents are lower than two
times the radius $r$. If this is the case it means that the $i$'th agent cannot
generate a trajectory in between these agents, which can lead to a
local minima. Therefore is the agents that are too close combined into
one by generating the middle point between their positions and
generating a new radius. This makes a larger circle where the two
agents are in the subset. This circle will be larger depending on the
wanted safety radius thus rises the need to recheck the potential
field again after have generated a new combined agent. If the radius
of the new agent places it close to one of the single agents, these
also might need to cluster. Thus the algorithm needs to run until no
distances between agents are less than two times the radius.

@@

\section{Results}
The potential field control system consists of multiple elements
as seen with the flow which is illustrated on the block diagram on
figure~\vref{fig:potentialfield_block}.
\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{fig/potentialfield_block}
\caption{Block diagram showing the iteration process of using the
potential fields for computation of the input vector}
\label{fig:potentialfield_block}
\end{figure}
The first block is the potential field generator. This is the
potential field calculation to compute the magnitude of the global
potential field. This information is passed to a trajectory generator,
which generates the reference trajectory. This reference trajectory is
where the $i$'th agent needs to move. This is passed to the controller
of the vessel, which then computes the input to the actuators on the
vessels, which in this case is done via a linear controller, which has been developed based on a linearized version of the vessel around its nominal operating point. The position of the vessels are then fed back, both to the
potential field calculation, the trajectory generation and the
controller. The potential field needs to be calculated from the
vessels relative position, the trajectory generation needs the
position for the intermediate reference position and the controller
will need it for i.e. error calculations.

@@

A simulation of the algorithm with the dynamics of the AAUSHIP can be seen on figure \ref{fig:potform}.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=\linewidth]{fig/lawn-bar-formation}
  \caption{Four agents are placed relative to the middle point of the
	formation, the virtual leader. This leader moves at the trajectory
with the waypoints, but only changes to the next waypoint if the
agents are in formation. The blue circles with the red plus signs are
the waypoints of the virtual leader. The other paths are computed from
this and the FRP.}
  \label{fig:potform}
\end{figure}
The red crosses are waypoints that have been targeted as the next waypoint to reach. The line connecting those waypoints are the virtual leader movement, which changes position from waypoint to waypoint to generate the straight line segments for the formation to follow. Every of the four agents have a relative position placement to the virtual leader, the agents positions are $p_{ij}$ and given as $p^n_{vl} + \text{offset}$ and the position of the virtual leader is given as $p^n_{vl}$. The ships are shown as yellow ships and the ships in formation is connected with a red line.
